### 2016-08-01 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers

\item Event selection cuts: the committee acknowledges the numerous studies 
(variation of cuts) that have been performed. It is not fully convinced, 
however, that there is no remaining background (other than $\pi^{0}$s only) in 
either channel, and about the argument on the statistics (for cutting tails).  
Consequently, it is requested:
\begin{enumerate}
\item To show plots of correlations between exclusivity cuts:
\begin{enumerate}
  \item 2D missing $ep\gamma X$ M2 vs $\Delta \phi$: is there a gain to be 
     expected by a contour cut? If yes, implement. Shown in figure 
     \ref{fig:2d_delta_phi_MM2_InCoh}
    \begin{figure}[!h]
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis.png}
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis_with.png}
    \caption{ $\Delta \phi$ vs. $MM^{2}_{ep\gamma X}$ before (left) and 
    after (right) the exclusivity cuts.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions for the different cut 
    width on $e^{4}He\gamma X$ missing mass squared. }
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $ep\gamma X$ missing mass squared.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g.  1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).

   \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/BSA_incoherent_epMM.png}
    \caption{ The integrated, over $Q^{2}$, $x_{B}$, and $-t$, incoherent 
    beam-spin asymmetries as a function of $\phi$ for the different cuts on 
 $epX$ missing mass squared.}
    \label{fig:BSA_incoherent_epMM}
    \end{figure}

    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/epMM2_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $epX$ missing mass squared.}
    \label{fig:epMM2_incoh_exc_cuts}
    \end{figure}

@@

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.
    \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
 background subtraction.  On bottom: the difference between the two asymmetries 
 as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

@@

 \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 
    when not applying any finite bin size correction. But again, in view of the 
    size of statistical and systematic errors, would accept that.
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.
\item ...
   \end{enumerate}

@@

\item Request to see the very first draft of the publication.
\end{enumerate}

>>>>

\item Event selection cuts: the committee acknowledges the numerous studies 
(variation of cuts) that have been performed. It is not fully convinced, 
however, that there is no remaining background (other than $\pi^{0}$s only) in 
either channel, and about the argument on the statistics (for cutting tails).  
Consequently, it is requested:
\begin{enumerate}
\item To show plots of correlations between exclusivity cuts:
\begin{enumerate}
  \item 2D missing $ep\gamma X$ M2 vs $\Delta \phi$: is there a gain to be 
     expected by a contour cut? If yes, implement.\\
    \textcolor{blue}{The results are shown in figure 
       \ref{fig:2d_delta_phi_MM2_InCoh} before and after the exclusivity cuts.  
    No clear dependence is observed.}  \begin{figure}[!h]
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis.png}
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis_with.png}
    \caption{ $\Delta \phi$ vs. $MM^{2}_{ep\gamma X}$ before (left) and 
    after (right) the exclusivity cuts.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
     \textcolor{blue}{The coherent and the incoherent distributions are 
        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
     respectively. No correlations were observed in the coherent DVCS channel, 
  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
  case?.}
     \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions corresponding to different cuts 
    on $e^{4}He\gamma X$ missing mass squared.}
    \label{fig:exc_Coh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $ep\gamma X$ missing mass squared.}
    \label{fig:exc_InCoh}
    \end{figure}

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g. 1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).\\
   \textcolor{blue}{The reconstructed incoherent asymmetries are presented in 
      figure \ref{fig:BSA_incoherent_epMM} with the associated exlcusive 
      distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. The different 
   tail cuts show no major effects on the reconstructed ALU.}

   \begin{figure}[tbp]
    \centering
    \includegraphics[height=8.6cm]{fig/BSA_incoherent_epMM.png}
    \caption{ The integrated, over $Q^{2}$, $x_{B}$, and $-t$, incoherent 
    beam-spin asymmetries as a function of $\phi$ for the different cuts on 
 $epX$ missing mass squared.}
    \label{fig:BSA_incoherent_epMM}
    \end{figure}

    \begin{figure}[tbp]
    \centering
    \includegraphics[height=14.6cm]{fig/epMM2_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $epX$ missing mass squared.}
    \label{fig:epMM2_incoh_exc_cuts}
    \end{figure}

@@

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.\\
    \textcolor{blue}{We implemented a 4D ratio R for the background 
       subtraction. The difference between the reconstructed ALU with 2D and 4D 
       background subtraction are presented in figures \ref{fig:coh_binning} 
       and \ref{fig:incoh_binning} for the coherent and the incoherent DVCS 
       channels. Even though the 2D was a good a pproximation, a 4D subtraction 
    is applied on the final results.} 
    \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
 background subtraction.  On bottom: the difference between the two asymmetries 
 as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

@@

 \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 
    when not applying any finite bin size correction. But again, in view of the 
    size of statistical and systematic errors, would accept that.

\item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.

@@

\item Request to see the very first draft of the publication.
